|

### 2021-03-17 documentation/readme.Rmd
Editted poll of polls section

**British Poll of Polls, `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`:**

- **`r txt_dta$party[1]`:** `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
- **`r txt_dta$party[2]`:** `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
- **`r txt_dta$party[3]`:** `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`

>>>>

British Poll of Polls, `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`:

- `r txt_dta$party[1]`: `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
- `r txt_dta$party[2]`: `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
- `r txt_dta$party[3]`: `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`
